# Week 6 Short Answer Questions

## Leqi Zhao

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

# 12.1

```{r}
data(BabyNames)
BabyNames %>% group_by(sex,name) %>%
  summarize(total_count = sum(count)) %>%
  filter(rank(desc(total_count))<=5)
```


# 12.2

```{r}
PopularCounts <- BabyNames %>%
  group_by(name, year) %>%
  summarize(total_count = sum(count)) %>%
  group_by(year) %>%
  mutate(frac_in_top_100 = ifelse(rank(desc(total_count))<=100, "yes", "no"))

GlyphReady <-
  PopularCounts %>%
  spread(frac_in_top_100, total_count) %>%
  mutate(frac_in_top_100 = yes / (yes + no))

ggplot() +
  geom_point(data = GlyphReady, aes(x= year, y = frac_in_top_100))

```


# 12.3

a. transformation function \\
b. transformation function \\
c. summary function \\
d. transformation function \\
e. transformation function \\
f. transformation function \\
g. transformation function \\
h. transformation function \\

# 13.1

8 vertices, 9 edges.

# 13.2

vertices: B,A,C,D, Table 2 shows it correctly. Table 1 points to the wrong direction, there's no connection between B and C. Table 3 has ACD wrong. We should start from C to D, instead of ACD.

# 13.3

Table 2

# 13.4

exports is mapped to the size of the letter. pop is mapped to the shape. 

# 14.1

```{r}
library(mosaicData)
data(CPS85)
CPS85 %>%
  ggplot(aes(y = wage, x = sex)) +
  geom_boxplot(aes(color = sex, fill = sex), 
               position = position_dodge(width=0.8),
               outlier.size=1, outlier.colour="gray")
```


# 14.3

The most likely height for women will be around 1.62, and for men will be around 1.75.

# 14.7

```{r}
CPS85 %>%
  ggplot(aes(y = wage, x = educ, color = sex)) +
  stat_smooth(se = FALSE) +
  geom_point(aes(fill = sex), 
               position = position_dodge(width=0.8),
               outlier.size=1, outlier.colour="gray")
```


# 14.10

```{r}
data(Galton)
Galton %>%
  ggplot(aes(x= height, group= sex)) +
  geom_density(aes(color = sex, fill = sex), alpha = 0.5)

```

