# Week 5 Project

## Leqi Zhao

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(dplyr)
library(data.table)
```
<!-- put your content after this line -->

# Stock and Dividends

TM has bigger income buying and selling a stock certificate. \

Having larger income from buying and selling a stock certificate contantly can also have larger income from dividends

```{r}
companies <- c("A", "G")
Prices <- 
  read_stock_prices(companies, what="daily",
                  start_year=2000, end_year=2015) 

```

```{r}
ggplot() +
  geom_point(data = Prices, aes(x= date, y = close, col = as.factor(company)))
```

# Buy/Sell Profit

```{r}
Actions <- data.frame(action = c("buy","sell"), date = c("2012-06-05",  "2014-12-30"))
Actions$date <- as.Date(Actions$date)
```

```{r}
combined <- Actions %>%
  left_join(Prices, c("date" = "date")) %>%
  select(company, action, close) %>%
  spread(key = action, value = close) %>%
  group_by(company) %>%
  summarise(profit = sell-buy, percent = (sell-buy)/buy)
combined  
```


# Indexing Prices

Roughly 2004-5-30 is the reference data in Figure 3.

```{r}
ref_date <- ymd("2012-06-05")
Reference <-
  Prices %>% 
  filter(date==ref_date) %>%
  select(company, standard=close)
```

```{r}
combined2<- Prices %>%
  full_join(Reference, by = c("company" = "company")) %>%
  mutate(ratio = close/standard)
```

# Dividends

```{r}
Dividends <- 
  read_stock_prices(companies, what="dividends") 
```

## Extract dates

```{r}
Actions_new <- Actions  %>% spread(key = action, value = date)
combined3 <- Dividends %>%
  filter(date > Actions_new$buy & date < Actions_new$sell)
combined3
```

## Find the dollar amount of each dividend payment for one share of stock

```{r}
dividend_dollar <- combined3 %>%
  left_join(Prices, by = c("company" = "company", "date" = "date")) %>%
  mutate(dividend_dollar_amount = dividends * close)
dividend_dollar
```

## total amount of dividends for each company during the period of interest

```{r}
dividend_dollar %>% group_by(company) %>% summarise(total_dividend = sum(dividend_dollar_amount))
```


