# Week 2 Short Answer Questions

## Your name should appear here!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->


# Short answer questions
*1.1, 1.2, 1.4, 1.5
*2.2, 2.3, 2.4, 2.6, 2.7, 2.8, 2.8, 2.9, 2.10
*3.1, 3.2, 3.3, 3.4, 3.5, 3.6
*4.1, 4.2, 4.3, 4.4, 4.5

# 1.1

(a):3  (b):2 (c):1 (d):1 (e):2

# 1.2
The data is not arranged in a precisely defined pattern. For president, "Lincoln, Abraham" is in a different format from other values, for in office column, "1837 to 1841" is also different. "It depends" is also different from other number of states values.

# 1.4

## (1) variables in each table:

A: Year Algeria Brazil Columbia
B: Country Y2000 Y2001
C: Country Year Value

## (2)

A: a year
B: a country
C: a country in a year

# 1.5

## (1) 
7 variables

## (2)
Each case represents metadata for an airport

## (3) 

faa FAA airport code: numerical
name: categorical
lat,lon: numerical
alt : numerical
tz: numerical
dst: categorical
tzone: categorical

# 2.2

3. the name of an argument in a named argument

# 2.3

The Current Population Survey (CPS) is used to supplement census information between census years. These data consist of a random sample of persons from the CPS85, with information on wages and other characteristics of the workers, including sex, number of years of education, years of work experience, occupational status, region of residence and union membership.

# 2.4

To ask a topic, you should double quote the topic to be a string.

# 2.6

first-essay: can't contain "-" in object name
small sample: can't do blank space
FuNcTiOnLiSt: capital for each letter matters, this is different from functionList in R
sqrt(): () is illegal (sqrt() is a function in R)

# 2.7

```{r}
data(flights, package="nycflights13")
```

19 variables, 336776 cases, a case is for each flight

```{r}
numerical <- names(flights)[c(1:9,11, 15:19)]
paste0(numerical, " is numerical")
categorical <- names(flights)[c(10,12:14)]
paste0(categorical, " is categorical")
```
air-time: Amount of time spent in the air, in minutes \\
distance :Distance between airports, in miles \\


# 2.8

a. 3
b. 1
c. 4
d. 2
e. 5



# 2.9 

. _ can be used in name of R object


all characters can be used in string.


# 2.10

CountryData has 76 variables. \\
tfat: mass of trunk fat. \\
WorldCities: 23018 cases. \\
BabyNames' 3rd name: count \\
party in RegisteredVoters: Party affiliation: DEM=Democratic, LIB=Libertarian,REP=Republican,UNA=Unaffiliated \\

# 3.1

```{r}
# 1
fireplace = data.frame(x = 1, y = 1:10 )
# 2
fireplace = function(x){
  return (x)
}
# 3
a = function(fireplace = 1){
  return(fireplace)
}
# 4
fireplace = 1
```


# 3.2

You should put BabyNames between pipelines like Result <- BabyNames %>% filter...

# 3.3

To ask a topic, you should double quote the topic to be a string.

# 3.4

1 b 2 a 3 c 4 a 5 a 6 c 7 c 8 a 9 d 10 a 11 c 12 a 13 a 14 d 15 d 16 a 17 d 18 a 19 d

# 3.5

brainwt: brain weight in kilograms \\
83 cases \\
Each case is a mammal \\
vore :carnivore, omnivore or herbivore \\



# 3.6
c

# 4.1

*one*
**two**
* three
# Four
`five`
## Six
[seven](http://tiny.cc/dcf/index.html)

# 4.2

(a) should use ` instead of '
(b) should use ` instead of "
(c) should have three ` in the end
(d) should return the next two lines
(e) should have three ` in the end instead of four

# 4.3

### An Introduction
Arithmetic is *easy*! For instance 
```{r}
3+2
```

# 4.4

1. neither 2. file 3. neither 4. neither 5. url 6. url

# 4.5

```{r}
library(DataComputing)
```

