# Week 3 Short Answer Questions

## Leqi Zhao

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

# 5.1

```{r}
library(mosaicData)
library(DataComputing)
data("CPS85")

# You have to dodge the position. This can be solved if I use the ggplot2 package.
# barGraphHelper(CPS85) 
```


# 5.2

```{r}
data(HappinessIndex)
HappinessIndex %>%
  WorldMap(key="country",fill="corruption")
```



# 6.5

b

# 6.6

d

# 6.7

b

# 6.8

```{r}
Small <-
   NCHS %>%
   sample_n(size=5000)
scatterGraphHelper(Small)
```

Age and followup is the frame for this plot. 

# 7.1

a. mean
b. mutate
c. arrange
d. filter
e. select
f. group_by, summarise, max

# 7.4

a. You don't need double quote
b. You don't have to include Tmp in the last line
c. You have to assign BabyNames with values


# 7.5

a

BabyNames %>%
  filter(sex = "F")

b

BabyNames %>%
  filter(sex = "F") %>%
  arrange(year)

c

BabyNames %>%
  filter(sex = "M")

d

BabyNames %>%
  summarise(total = sum(count))

e

BabyNames %>%
  select(name, count)

# 7.7

a

BabyNames %>%
  group_by(BabyNames, year, sex) %>% summarise(BabyNames = BabyNames, total = sum(count))
 
b

ZipGeography <- select(State, Population) %>%
     group_by(State) %>%
     summarise(pop = sum(Population))


c

Minneapolis2013 <- group_by(First) %>%
     summarise(voteReceived = n())

d

Minneapolis2013 <- group_by(First)  %>% 
     summarise(votesReceived = n()) 

# 7.11

a It shows the population and mean age of females and males separately.
b It shows the population and mean age of people with different diagnosis.
c It shows the population and mean age of females and males with different diagonosisseparately.
d It shows the population and mean age of people in every different age and every different diagnosis separately.
e.It shows the population and mean age of people in every different age separately.

# 7.12

1. nrow()
2. names()
3. summary()
4. help()
5. group_by()
6. summarise()


